Cryptographic assurance of secrecy and fairness in voting

### 2012-12-08 paper/paper.tex
Move a paragraph in the introduction
Correct terminology

Once votes have been collected, it is the responsibility of the state to tally votes for the various
candidates in a race and publish \emph{accurate} tallies. Generally, the electorate is reliant on
\emph{someone} to provide these tallies. But it is much less common for voters themselves to have
the opportunity to verify that the votes were tallied \emph{exactly} as they were cast.

>>>>

Once votes have been collected, it is the responsibility of the election authority to tally votes for the various
candidates in a race and publish \emph{accurate} tallies. Generally, the electorate is reliant on
\emph{someone} to provide these tallies. But it is much less common for voters themselves to have
the opportunity to verify that the votes were tallied \emph{exactly} as they were cast.
